---
title: "Assignment 4"
author: "seungjoon yoo"
date: "8/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE )
```
```{r}
library(tidyverse)
library(dplyr)
library(readxl)
```

This is my R workdown for Assignment 4.

First, import the congressional_hearings dataset.

```{r}
hearingData <- read_excel("/Users/seungjoonyoo/Desktop/DACSS601_Data Science Fundamentals/4. Datasets/congressional_hearings.csv.xlsx")
```

```{r}
str(hearingData)
```

Create a subdata,"civil", which is categorized by the major topic == 2. Then, select
"filter_House", "Sessions", "Days" and "Committee1" columns. Since the filter_House variable is a numeric value, I converted it into a factor using as.factor(). Same goes to Committee1 variable. Also delete the NAs using na.omit()

```{r}
civil <- hearingData %>%
  filter(`majortopic` == 2) %>%
  select(filter_House, Sessions, Days, Committee1 ) %>%
  mutate(filter_House = as.factor(filter_House),
         Committee1 = as.factor(Committee1)) %>%
  na.omit()
summary(civil)
str(civil)
```

First, find the number of committees that house representatives created
```{r}

ggplot(civil, aes(x=filter_House))  + 
  geom_bar()
```

In order to see how Sessions is distributed, I used geom_histogram()
```{r}
civil %>%
  filter(Sessions > 0) %>%
  ggplot(aes(x=Sessions)) +
  geom_histogram(binwidth = 1)
```

I came with three hypotheses that 1. committees that are created by house representatives are more likely to have bigger sessions; 2. committees that are created by house representatives are more likely to have longer Days; 3.  While it may sound pretty intuitive, but for the practice purpose, I wanted to check whether more sessions will indeed take longer days. In order to visualize their relationships; I used geom_boxplot() for all three hypotheses.

```{r}
civil %>%
  filter(Sessions > 0) %>%
  ggplot(aes(x=filter_House, y=Sessions)) + 
  geom_boxplot()

civil %>%
  filter(Sessions > 0) %>%
  ggplot(aes(x=filter_House, y=Days)) + 
  geom_boxplot()

civil %>%
  filter(Sessions > 0 ) %>%
  ggplot(aes(x=Sessions, y =Days)) +
  geom_jitter() +
  geom_smooth()

civil %>%
  filter(Sessions > 0 ) %>%
  ggplot(aes(x=Sessions, y =Days, col = filter_House)) +
  geom_jitter() +
  geom_smooth()
```

Unfortunately, all my hypotheses don't seem to be correct